Synthesizing by means of mice with partially synthetic data rules

### 2021-01-23 mice_synthesizing/synthesizing_partially_synthetic_data_rules.Rmd

@@

Note the fact that the confidence interval coverage of the bootstrapped datasets is somewhat below the nomimal $95\%$ level, due to the fact that the bootstrap variance is somewhat larger than the estimated variances.

>>>>

To assess the quality of the synthetic data, we look at the results and the confidence interval coverage of the regression coefficients of the regression model `wgt ~ age + hgt` of 500 synthetic versions of the `boys` data.

@@

Note the fact that the confidence interval coverage of the bootstrapped datasets is somewhat below the nominal $95\%$ level, due to the fact that the bootstrap variance is somewhat larger than the estimated variances.
